Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-04-26 main_paper.tex
Tweak notation for proof of first theorem
Our notation didn't distinguish between the estimate of the first derivative
of the conditional expectation using a 1st order vs 2nd order expansion. I've
updated the paper to include that distinction. It changes the notation definitions
at the start of the appendix as well as the proof of the first theorem.

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\ \hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation}
  \label{eq:5}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
``$-$'' for ``$+$.''

>>>>

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
\end{align*}
and
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_{-,2}^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
``$-$'' for ``$+$.''
